The Environment and Structure of Massive Central Galaxies using the Subaru Hyper Suprime-Cam Survey

### 2016-09-30 draft/ms.tex
Recent update of draft and notebooks

\documentclass[preprint]{aastex}
\usepackage{emulateapj5}
\usepackage{apjfonts}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{CJK}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\bibliographystyle{apj}

\input psfig.tex

@@

\newdimen\digitwidth    % These five lines change the meaning of
\setbox1=\hbox{0}       % " in the same way, so that it leaves as
\digitwidth=\wd1        % much space as a digit. (Note: All digits
\catcode`"=\active      % are the same width).

% Luis's Definitions
\def\arcsec{{\prime\prime}}
\def\arcmin{{\prime}}
\def\degree{{\circ}}
\def"{\kern\digitwidth}
\def\h{\hskip -3 mm}
\def\aa{{A\&A}}
\def\aas{{ A\&AS}}
\def\aj{{AJ}}
\def\al{$\alpha$}
\def\bet{$\beta$}
\def\amin{$^\prime$}
\def\annrev{{ARA\&A}}
\def\apj{{ApJ}}
\def\apjs{{ApJS}}
\def\asec{$^{\prime\prime}$}
\def\deg{$^{\circ}$}
\def\ddeg{{\rlap.}$^{\circ}$}
\def\dsec{{\rlap.}$^{\prime\prime}$}
\def\cc{cm$^{-3}$}
\def\etal{{\ et al.~}}
\def\flamb{erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$}
\def\flux{erg s$^{-1}$ cm$^{-2}$}
\def\fnu{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$}
\def\hst{{\it HST}}
\def\kms{km s$^{-1}$}
\def\lamb{$\lambda$}
\def\lax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$<$}}}$}}
\def\gax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$>$}}}$}}
\def\simlt{\lower.5ex\hbox{$\; \buildrel < \over \sim \;$}}
\def\simgt{\lower.5ex\hbox{$\; \buildrel > \over \sim \;$}}
\def\micron{{$\mu$m}}
\def\mnras{{MNRAS}}
\def\nat{{Nature}}
\def\pasp{{PASP}}
\def\perang{\AA$^{-1}$}
\def\peryr{yr$^{-1}$}
\def\pp{\parshape 2 0truein 6.1truein .3truein 5.5truein}
\def\reference{\noindent\pp}
\def\refindent{\par\noindent\parskip=2pt\hangindent=3pc\hangafter=1 }
\def\sb{mag~arcsec$^{-2}$}
\def\solum{$L_\odot$}
\def\solmass{$M_\odot$}
\def\sigs{$\sigma_*$}
\newcommand{\lt}{<}
\newcommand{\gt}{>}

%Song Huang's definition 
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}

@@

\slugcomment{Draft version 0}
\shorttitle{ENVIRONMENT DEPENDENCE OF MASS-SIZE RELATION}
\shortauthors{HUANG ET AL.}

@@

\title{The Environmental Dependence of Structures for Massive Galaxies
from the Hyper-Suprime Camera Survey}

\author{Song Huang (黄崧)\altaffilmark{1} Alexie Leauthaud\altaffilmark{1}, 
Kevin Bundy\altaffilmark{1}, and You}
\date{}

\altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the
Universe, Todai Institutes for Advanced Study, the University of Tokyo (Kavli
IPMU, WPI), Kashiwa 277-8583, Japan}

@@

  Many recent observations and numerical simulations suggest that nearby
  massive, early-type galaxies are formed through a ``two-phase'' process.  In
  the proposed second phase, the extended stellar envelope was accumulated
  through many dry mergers. (XX TODO)

@@

\section{Introduction}

\section{Sample and Data Reduction}

>>>>

\documentclass[preprint]{aastex}

% Packages
\usepackage{emulateapj5}
\usepackage{apjfonts}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{CJK}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage[usenames]{color}

% Package Settings
\bibliographystyle{apj}
\hypersetup{colorlinks=true,
            citecolor=cyan,
            linkcolor=cyan,
            filecolor=magenta,      
            urlcolor=cyan}
\urlstyle{same}

% Figure extention
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\input psfig.tex

@@

% Song Huang's definition 
\def\arcsec{{\prime\prime}}
\def\arcmin{{\prime}}
\def\degree{{\circ}}
\def\h{\hskip -3 mm}
\def\aa{{A\&A}}
\def\aas{{ A\&AS}}
\def\aj{{AJ}}
\def\al{$\alpha$}
\def\bet{$\beta$}
\def\amin{$^\prime$}
\def\annrev{{ARA\&A}}
\def\apj{{ApJ}}
\def\apjs{{ApJS}}
\def\asec{$^{\prime\prime}$}
\def\deg{$^{\circ}$}
\def\ddeg{{\rlap.}$^{\circ}$}
\def\dsec{{\rlap.}$^{\prime\prime}$}
\def\cc{cm$^{-3}$}
\def\flamb{erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$}
\def\flux{erg s$^{-1}$ cm$^{-2}$}
\def\fnu{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$}
\def\hst{{\textit{HST}}}
\def\kms{km s$^{-1}$}
\def\lamb{$\lambda$}
\def\lax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$<$}}}$}}
\def\gax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$>$}}}$}}
\def\simlt{\lower.5ex\hbox{$\; \buildrel < \over \sim \;$}}
\def\simgt{\lower.5ex\hbox{$\; \buildrel > \over \sim \;$}}
\def\micron{{$\mu$m}}
\def\mnras{{MNRAS}}
\def\nat{{Nature}}
\def\pasp{{PASP}}
\def\perang{\AA$^{-1}$}
\def\peryr{yr$^{-1}$}
\def\reference{\noindent\pp}
\def\refindent{\par\noindent\parskip=2pt\hangindent=3pc\hangafter=1 }
\def\sb{mag~arcsec$^{-2}$}
\def\lsun{$L_\odot$}
\def\msun{$M_\odot$}
\def\sigs{$\sigma_*$}
\newcommand{\lt}{<}
\newcommand{\gt}{>}

\def\etal{{\ et al.~}}
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}
\def\redm{\texttt{redMaPPer}}
\def\cmodel{\texttt{cModel}}
\def\redbcg{{$\lambda \ge 30$}}
\def\nonbcg{{$\lambda < 20$}}
\def\logms{{$\log (M_{\star}/M_{\odot})$}~}
\def\mstar{{$M_{\star}$}~}
\def\logmh{{$\log (M_{\mathrm{Halo}}/M_{\odot})$}~}
\def\mcmodel{{$M_{\star,\mathrm{cModel}}$}~}
\def\mtot{{$M_{\star,100\mathrm{kpc}}$}~}
\def\minn{{$M_{\star,10\mathrm{kpc}}$}~}
\def\m2l{{$M_{\star}/L_{\star}$}~}
\def\rbcg{\texttt{redBCG}}
\def\nbcg{\texttt{nonBCG}}

% Commenting:
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}

@@

\slugcomment{Draft version -1}
\email{song.huang@ipmu.jp}
\shorttitle{ENVIRONMENT DEPENDENCE OF MASS-SIZE RELATION}
\shortauthors{HUANG ET AL.}

@@

\title{The Environment and Structure of Massive Central Galaxies
using the Subaru Hyper Suprime-Cam Survey}

\author{Song Huang (黄崧)\altaffilmark{1} 
        Alexie Leauthaud\altaffilmark{1}, 
        Kevin Bundy\altaffilmark{1},
        Michael Strauss\altaffilmark{2},
        Yen-Ting Lin\altaffilmark{3},
        Rachel Mandelbaum\altaffilmark{4}
        }
\date{}

\altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the 
    Universe, The University of Tokyo Institutes for Advanced Study, 
    the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan}
\altaffiltext{2}{Princeton University Observatory, 
    Peyton Hall, Princeton, NJ 08544, USA}
\altaffiltext{3}{Institute of Astronomy and Astrophysics, Academia Sinica, 
    P.O.~Box 23--141, Taipei 10617, Taiwan}
\altaffiltext{4}{Carnegie-Mellon University \todo{correct affiliation here}}

@@

    Although the environmental dependence of structures for massive central 
    galaxies is predicted by the promising hierarchical assembly model, 
    observations at low redshift seem to find no convincing evidence for that. 
    With the help of deep $i$-band images of a large sample of massive central 
    galaxies at $0.3 < z < 0.5$ from the Subaru Hyper Suprime-Cam (HSC) survey, 
    we map their stellar mass distributions out to radius larger than $100$ kpc, 
    and discover subtle, but systematic and robust structural differences that 
    depend on halo mass. 
    At fixed stellar mass within 100 kpc, the massive central galaxies in more 
    massive ($M_{200,c}$ \gax $1.6\times 10^{14} M_{\odot}$) halos have a 
    slightly flattened inner profile within $\sim 15$-$20$ kpc, and a more prominent 
    outer envelope compared to ones in less massive 
    ($M_{200,c}$ \gax $8.7\times 10^{13} M_{\odot}$) halos.
    For centrals with $M_{\star} > 10^{11.5} M_{\odot}$, the ones in more massive 
    halos show very significant excess of mass in the outskirt when the two samples 
    are matched using proxies of mass assembled at $z > 1$. 
    Such differences are broadly consistent with richer recent merging history 
    for more massive halos. 
    We suggest that the relation between total stellar mass and mass within inner 5 
    or 10 kpc is potentially interesting for diagnosing the role played by host halo 
    in shaping the structures of massive central galaxies. 
    These results also highlight the importance of deep photometry and the usage of 
    detailed structural information in the study of the assembly history of galaxies.

    % We also show that the radial profiles of ellipticity and optical color, along with 
    % the preliminary weak lensing signals will enable us gain more insights about the 
    % evolution of massive galaxies.

@@

%% ------------------------------------------------------------------------------------ %% 
\section{Introduction}

    \plan{Scientific Background}
    \begin{itemize}
        \item \plan{Massive galaxies are important cosmic probe and unique labs to study 
            galaxy evolution.} 
        \item \plan{Briefly explain why massive early-type galaxies are important through 
            the difficulties of stellar-halo mass relation and stellar mass function at the 
            high-mass end.}
        \item \plan{Brief summary of the current understanding of their cosmic assembly 
            history.}
        \item \plan{Explain why we should care about the environment, and why we expect to 
            see some environmental dependence in the structure and other properties of
            massive galaxies.}
        \item \plan{Brief review of the current observations.  It is still not clear 
            whether there is a clear environmental dependence.}
    \end{itemize}

    \plan{Observational difficulties (a.k.a Why we need HSC)}
    \begin{itemize}
        \item \plan{Explain why it is important to study the mass distribution of 
            massive galaxies out to large physical radius; and, given their unique light 
            profiles, why it is more difficult to study them compared to late-type 
            galaxies.}
        \item \plan{Very brief summary of past observational efforts, and why they are not 
            good enough (Not enough number of really massive galaxy; Shallow images; 
            Background subtraction issue; and stacking analysis can be dangerous as while)}
    \end{itemize}

    \plan{Basic idea of this work}
    \begin{itemize}
        \item \plan{Here we take advantages of the ambitious Hyper-Suprime camera 
            survey\ldots}
    \end{itemize}

    To achieve this goal, we will select \logms$ > 11.5$ massive central galaxies within
    host halo mass larger and smaller than \logmh$= 14.0$ at $0.3 < z < 0.5$.  
    As both $M_{\star}$-$M_{\mathrm{Halo}}$ relation and stellar mass function are still
    quite uncertain at \logms$ > 11.5$, it is of great interest to investigate the
    structure of galaxies in this region carefully. 
    Under the adopted cosmology, $1.0^{\arcsec}$ equals 4.4 and 6.1 kpc at redshift 0.3 
    and 0.5.  
    Therefore, this redshift range enables us to reliable measure the total stellar mass 
    within the inner 5 to 10 kpc (where the ``in-situ'' component should still dominates) 
    of massive galaxies at the high redshift end assuming the typical seeing of HSC data. 
    At the same time, the depth of the HSC image allows to map the stellar distribution 
    of these galaxies out to $\sim 100$ kpc at $z\sim 0.5$.  
    Within these stellar mass and redshift range, we can select a large sample of 
    galaxies from the current $\sim 100$ square degree of HSC data, and safely ignore 
    significant mass growth and structural evolution (no star formation, 
    lower merger rate \etal~e.g.\ \citealt{Bellstedt2016}, \citealt{Inagaki2015}; 
    but also see \citealt{Bai2014}; more discussion about this in Section~5).

    The paper is organized as follows. Section~2 gives a brief overview of the HSC
    observation and data reduction.  We will also summarize the process of sample
    selection.  In Section~3, we will describe the method for deriving the stellar mass 
    surface density profile.  The main results are summarized in Section~4.  Section~5 
    provides discussions of the assumptions used in this work, the potentially interesting
    physical implications, and several future improvements, ending with a summary in
    Section~6.

    All the magnitudes used here are in AB system (\citealt{Oke1983}), and are corrected 
    for Galactic extinction using calibrations from \citet{Schlafly11}.
    Within this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_m=0.3$, 
    and ${\Omega}_{\lambda}=0.7$.

%% ------------------------------------------------------------------------------------ %%

\section{Data And Sample Selection}

\subsection{The Hyper Suprime-Cam Survey}

    The Subaru Strategic Program (SSP, \addref) makes use of the new prime-focus camera,
    the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 8.2-m Subaru
    telescope at Mauna Kea.  
    Taking advantage of the large field of view (FoV;~1.5 deg in diameter) of HSC, this
    ambitious multi-layer photometric survey will cover $\sim 1400$ deg$^2$ of sky in 5
    broad bands (\textit{g r i z Y}) to the depth of $r \sim 26$ mag in the \texttt{WIDE}
    part in the next few years.  
    This work is based on the internal data release \texttt{S15B}, which covers $\sim 100$
    square of degree of sky in all 5-band to the required depth of \texttt{WIDE} survey.  
    The regions covered by this release are overlapped with several previous spectroscopic
    survey (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).

    The data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large Synoptic
    Survey Telescope (LSST) pipeline (e.g.\ \citealt{Ivezic2008}; \citealt{Axelrod2010}),
    modified for use with Suprime-Cam and Hyper Suprime-Cam.  
    \texttt{hscPipe} first bias subtract, flat field, model background, and perform object
    detection and measurement on the single exposure data. 
    Then, different exposures are warped onto a common World Coordinate System (WCS) and
    combined into final images with improved signal-to-noise ratio (SNR) after astrometric
    and photometric calibration.  
    The pixel scale of the combined images is $0.168^{\arcsec}$.  
    The photometric calibration is based on data obtained from the Panoramic Survey 
    Telescope and Rapid Response System (Pan-STARRS) 1 imaging survey 
    (\citealt{Schlafly2012}, \citealt{Tonry2012}, \citealt{Magnier2013}). 
    To achieve consistent deblending and photometry across all bands, the \texttt{hscPipe}
    will perform multi-band post-processing on the combined images.  
    The footprints and peaks of detected sources on each band will be merged into a single
    catalog.    
    This consistent set of peaks and footprints is used as starting point for deblend and
    measure objects on the combined images of each band.  
    These measurements are then merged into a reference catalog.  After fixing the
    centroids, shape, and other non-amplitude parameters of every object in this catalog,
    \texttt{hscPipe} will derive forced photometry measurements at each band. 
    Details of \texttt{hscPipe} and the multi-band processing method will be presented in
    \addref~(Bosch\etal~in prep.).

    In Figure 1, we compare the false color ({\tt gri}) images of nearby massive
    galaxies from both SDSS and HSC surveys.  
    The RGB images are generated using similar scaling and color schemes, and clearly
    demonstrate the capability of HSC to map the stellar distribution out to the very 
    outskirt of these massive galaxies, where important fossil records about their 
    recent assembly history are stored.   
    In $i$-band (ignoring the slight difference in filter response curve), the HSC
    \texttt{WIDE} image is on average $3.0$-$4.0$ magnitude deeper than SDSS, which 
    gives us significant advantage in studying massive ETGs given their extended, shallow 
    outer surface brightness profiles.

    Motivated by the requirement of weak lensing analysis, the $i$-band data typically has
    the best seeing in all five bands (the median seeing is around 
    FWHM$\sim 0.7^{\arcsec}$).
    Therefore, we will mostly use the $i$-band images to study the structure of galaxies.

\subsection{\redm{} cluster catalog}

    In order to select the central galaxies from cluster level dark matter halos 
    (e.g.\ $> 10^{14} M_{\odot}$), we make use of the \redm{} cluster 
    catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (\texttt{v5.10}, e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}).
    These clusters are selected from the SDSS DR8 photometric data using overdensity of
    red-sequence galaxies. 
    For each cluster, the catalog provides robust estimations of photometric redshift
    $z_{\lambda}$ and richness $\lambda$, along with the best candidate of the central
    galaxy (the one with the highest central probability \texttt{P\_CEN}).
    Information about the identified member candidates is also provided separately. 
    Please see \citet{Rozo2014}, \citet{Rozo2015a}, \citet{Rozo2015b} for more details 
    about the performance of the \redm~cluster catalog.      
    Several works (e.g.\ \citealt{Saro2015}; \citealt{Farahi2016}; \citealt{Simet2016})
    have tried to calibrate the $M_{200, c}-\lambda$ relation using different methods.
    Despite the slightly different calibrations derived, it is safe to assume that most
    clusters identified by \redm~($\lambda > 20$) have $\log (M_{200,c}/M_{\odot}) \geq
    14.0$.  
    Considering the typical uncertainty of richness, and the fact that \redm~catalog
    starts to become incomplete toward low richness ($\lambda < 40$) end at $z > 0.33$, we
    will focus on the $\lambda > 30$ clusters in this work.  
    Based on the calibrations from \citet{Farahi2016} or \citet{Simet2016}, 
    such richness cut gives us haloes with 
    $M_{200c} \geq 1.56\pm0.35 \times 10^{14} M_{\odot}$ or 
    $M_{200c} \geq 1.60\pm0.11 \times 10^{14} M_{\odot}$.  
    Therefore, \redm~can provide us a sample of massive central galaxies in \logmh$\geq
    14.0$ haloes.

\subsection{Initial Selection of Massive Galaxies}

    We begin by making an initial selection of massive galaxies with reliable redshift from 
    the HSC survey.  
    The goal is to have a parent sample that contains a reasonably complete sample of 
    \logms$\geq 11.5$ galaxies at $0.3 < z < 0.5$. 
    According to Leauthaud\etal~(2016), such galaxies should have 
    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag.
    Therefore, we first select all galaxies with $i_{\mathrm{HSC, cModel}} \leq 21.5$ 
    \footnote{Difference of response curves between SDSS $i$ and HSC $i$ filter is tiny}
    in regions that are covered by all five bands, and have reached the expected depth 
    of \texttt{WIDE} survey.  
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects
    The HSC \texttt{cModel} photometry is similar to the SDSS \texttt{cModel} algorithm.  
    It fits the flux distribution of an object using a combination of de~Vaucouleur and 
    exponential components after the PSF convolution is considered.  
    For more details about the algorithm, please see Bosch\etal~in prep.~; and its 
    performance has been tested using synthetic objects (Huang\etal~in prep.~). 
    Although the overall performance of HSC \cmodel photometry is accurate down to very 
    faint magnitude, it tends to underestimate the total flux of massive ETGs 
    (will discuss this in details later). 
    This is partially caused by issues with deblending process (see more discussion in 
    Bosch\etal~in prep.~), but also reflects the intrinsic limitation of \cmodel, 
    as the real flux distributions of massive galaxies are often too extended to be 
    modeled this way at the depth of HSC images.  
    For this reason, we will perform careful photometric measurements to derive 
    more accurate total luminosity and stellar mass, and the sample selected here 
    serves as an initial one for us to work on.

    We select objects that are classified as galaxies, have well defined centroids, 
    are deblended successfully, and have \texttt{cModel} magnitudes in all five bands. 
    After a few more quality control criteria (saturation, cosmic-ray, optical artifact)
    are applied\footnote{each criterion affects less than 8\% of the entire sample}, 
    we select 1760845 galaxies in this sample that will be referred as \texttt{hscPho}. 
    %% Saved as "dr1_wide_galaxy_hscPho.fits"

    As reliable photometric redshift using HSC photometry is still a working progress, 
    we only use objects with either spectroscopic redshift or robust red-sequence 
    photo-$z$ from the \redm{} catalog.  
    We first match the \texttt{hscPho} sample with the external spec-$z$ catalog 
    compiled by HSC database\footnote{It is created by matching HSC objects with 
    public data of several spectroscopic surveys (e.g.\ SDSS/BOSS; GAMA). 
    Duplicated matches from different sources are merged through internal matching 
    using $0.5^{\arcsec}$ radius. 
    For each object, the quality information of the spec-$z$ from different catalogs are 
    homogenized into a single flag that indicates whether the redshift is secure, and 
    only secure spec-$z$ are used in this work.}
    %% This is catalog: "dr1_specz_use.fits"
    with a $1.0^{\arcsec}$ radius, and it leads to 116813 matched objects, and 
    42696 objects are at $0.3 \leq z \leq 0.5$.
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    Most of these redshifts come from either SDSS/BOSS or GAMA survey.
    For objects without external spec-$z$, we also match the sample with the \redm{}
    catalog, and add objects with useful red-sequence photo-$z$ ($z_{\lambda}$)
    back in.      
    Together, this gives us a sample of bright galaxies with useful redshift.

\subsection{Massive Central Galaxies from Low and High Mass Halos}

    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
    (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
    massive galaxies with \logms$ > 11.5$ are hosted by dark matter halos with a 
    large range of mass. 
    Although we can not measure halo mass for individual galaxy, we can still broadly 
    separate them into galaxies in small groups (\logmh$<14.0$) and large groups/clusters
    (\logmh$>14.0$), and investigate their stellar mass distributions.

    % We match this sample with the central galaxies of \redm~catalogs using a 
    % $1.0^{\arcsec}$ radius, and it results in 704 galaxies.  
    %% Saved as "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
    We first match the initial sample of massive galaxies with the central galaxies 
    in \redm{} catalog with $1.0^{\arcsec}$ radius, which results in 375 matched ones at 
    $0.3 \leq z \leq 0.5$.  
    We will refer this sample of \textbf{central galaxies in \logmh$\ge 14.0$ halos} as 
    \texttt{redBCG} in this work.
    A small fraction of \redm~centrals within HSC footprints do not have matched object 
    due to severe contamination from optical artifacts.
    Spec-$z$ is not available for 67 (17.9\%) of the sample, but their $z_{\lambda}$ 
    should be very accurate (median $|z_{\lambda} - z_{\mathrm{Spec}}|$ is about 0.01 
    for the ones with spec-$z$).
    The median richness ($\lambda$) of these clusters is $\sim 32$, corresponding to 
    halo mass of $M_{200,c}\sim 1.7\times 10^{14} h^{-1} M_{\odot}$. 
    Given the uncertainty of richness estimate using shallow SDSS photometry, we 
    mainly focus on the centrals of clusters that have $\lambda > 30$ 
    ($M_{200,c}> 1.7\times 10^{14} h^{-1} M_{\odot}$).
    %% Saved as "dr1_redbcg_use_sed5b.fits"

    Then, we matched the initial sample with both the central and satellite galaxy catalogs 
    of \redm{} using a physical radius of 2.5 Mpc and absolute redshift difference of 
    0.05 (using $z_{\lambda}$ for all members).  
    By removing all the matched objects, we aggressively exclude galaxies that are 
    associated with these massive halos.  
    The rest 29973 galaxies should mostly live in \logmh$< 14.0$ halos, and the real 
    \logms$ > 11.5$ ones among them should be dominated by central galaxies of these 
    halos as the satellite contamination is very low at such high mass end 
    (e.g.\citealt{vanUitert2016}).
    We will refer this sample of \textbf{central galaxies in \logmh$< 14.0$ halos} as 
    \texttt{nonBCG} later.
    %% Saved as "dr1_nonbcg_use_sed5b.fits"

    It is worth noting that, at $0.3 < z < 0.5$, most redshifts in both \texttt{redBCG} 
    and \texttt{nonBCG} come from GAMA and SDSS/BOSS survey.  
    The current sample partially overlaps with the GAMA survey, which reaches 
    to $\sim 19.8$ mag in $r$-band, and provides us unique spec-$z$ for 14\% of the 
    entire initial sample. 
    According to \citet{Taylor2011} (e.g.\ their Figure~6), at $z\sim 0.3$, the GAMA 
    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
    $10^{12.0}$\msun at $z\sim 0.5$. 
    Meanwhile, the BOSS survey provides us the majority of spec-$z$ in our samples.  
    Due to the complex selection criteria for different subsamples within the BOSS
    survey (e.g.\ the LOWZ and CMASS), its \mstar completeness is hard to estimate.  
    Recently, through comparing with the Stripe 82 Massive Galaxy Catalog
    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} suggests that the 
    BOSS spec-$z$ is about 80\% complete at \logms$\geq 11.6$ at $0.3 < z < 0.5$. 
    Despite the difference in photometry and stellar mass estimates, we can expect 
    our samples are reasonably complete above \logms$\geq 11.6$.
    We will further address the \mstar completeness issue more carefully with the 
    help of the photo-$z$ from the \texttt{S82-MGC} sample (see Section~4.3).

%% ------------------------------------------------------------------------------------ %%

\section{Measurements of 1-D Surface Brightness Profile}

\subsection{1-D Surface Brightness Profile}

    To estimate the total luminosity of massive galaxies, and measure their 
    one-dimensional stellar mass density profiles, we perform elliptical isophotes 
    fitting using the IRAF task \texttt{Ellipse} (Jedrzejewski 1987).  
    Compared to the popular two-dimensional model fitting method, the isophote fitting
    approach is much less sensitive to the choice of model type, number of components, 
    and initial guesses of free parameters; is also less affected by the uncertainties 
    of the sky background subtraction.  
    This is particularly important for the massive ellipticals in our sample.  
    The much deeper depth of the HSC images reveal much more extended structures, 
    but also make it impossible and inappropriate to fit these galaxies with single 
    \ser component as it often requires uncomfortably high \ser index (e.g.\ $>6.0$), 
    can not fit the center of massive galaxies well, and can not account for the 
    radial variation of ellipticity and position angle. 
    In principle, their surface brightness distributions can be described by models 
    with multiple components (e.g \citealt{Huang2013a}; \citealt{Huang2013b}).  
    However, these models still suffer from issues like sensitivity to background 
    subtraction, internal degeneracies of parameters, and choice of best number of 
    components.  
    Their robustness and physical meanings still deserve more investigations. 
    Therefore, we think the 1-D method suits the scientific goal of this work better.

    We first generate large cut-out images for galaxies in our samples, and make sure
    the image covers to at least 750 kpc from the center of the galaxy in radius, so 
    we can safely assume that we cover the entire galaxy while still have enough space 
    to estimate the background.  
    We also reconstruct the PSF model using the central coordinate of the galaxy, and 
    generate bad pixel mask. 
    We choose $i$-band as the default band to extract 1-D surface brightness profile 
    since it has the best seeing among all five bands, and can still serve as good 
    stellar mass distribution tracer at $0.3 < z < 0.5$.  
    Although $z$ and Y-band should suffer less from potential internal dust extinction
    and radial variation of mass-to-light ratio, the sky background is much higher in 
    these two bands, and the seeing conditions are often considerably worse than 
    $i$-band.

    Then we use a customized photometric procedures based on \texttt{SEP} Python library
    to create object mask before we run \texttt{Ellipse}.  
    The current HSC pipeline still has difficulties dealing with regions around bright 
    galaxies as the extended wings from bright objects result in overestimated S/N that
    leads to ``over-deblending'' issue.  
    Our customized pipeline is more flexible since we can run \texttt{SExtractor}-like
    measurements twice using different configurations for background subtraction, 
    detection, and deblending.  
    Global background, low-detection threshold, and conservative deblending help detects
    all the large, bright, or diffuse objects; while very small background box size and 
    aggressive deblending together can help detect the faint objects that are on the 
    extended envelope of bright galaxies or close to the galaxy center.  
    The catalogs from these two steps are merged after the target galaxy at the center 
    is identified and removed. 
    To mask out most fluxes from other objects, we convolved the pixel segmentation of 
    each object with a Gaussian kernel to increase its size.  
    Then, these expanded pixel segmentations are merged with the bad pixel mask into a 
    binary object mask.  
    This method works very well for early-type galaxy that has smooth structural 
    features.

    Meanwhile, we also generate a mask of all objects detected by above procedures with 
    a much more aggressive masking method (larger Gaussian kernel size).  
    We treat the unmasked pixels as ``sky pixels'', and rebin them using 6x6 box size.
    Then we use the median value of each box to generate the statistics of sky background.
    As expected, we often see negative median values in the distribution of sky pixels 
    around our massive galaxies as the HSC pipeline tends to slightly over-subtract 
    the background\footnote{This is similar to what happened to SDSS as shown in 
    \citealt{Blanton2011}, but at a lesser level.  The sky background of each CCD 
    is modeled using a Chebyshev-polynomial fit to the pixels that do not belong to 
    any object after they are smoothed}. 
    As this over-subtraction often leads to unphysical truncation of surface brightness 
    profile, we provide an ad-hoc fix using a \texttt{SExtractor}-like background model 
    created by \texttt{SEP} with 200$x$200 background box size.  
    Such model can capture the overall negative sky value, modify the median sky pixel 
    value very close to zero, and remove flux of nearby objects that are not perfectly 
    masked out by our object mask.

    Using the background-corrected cutout image and the mask, we run \texttt{Ellipse} 
    based on strategy very similar to \citep{Li2012}.  
    In summary, we start with \texttt{Ellipse} run with free central position and free
    geometry, then gradually constrain its behavior, and eventually extract 1-D 
    surface brightness profile along the major photometric axis using isophotes with 
    fixed center and shape.
    The 4th Fourier modes are included to fit the isophote better. 
    In this way, we can extract the radial changes of the photometric ``barycenter'', 
    ellipticity, position angle, and overall isophotal shape (more ``disky'' or 
    ``boxy'', e.g.\ \citealt{Kormendy2009}) of these galaxies at the same time.  
    At low surface brightness regime, the final profile can be sensitive to several 
    configuration parameters of \texttt{Ellipse}.  
    After some tests, we choose to use 0.1 dex in logarithm as the step in semi-major 
    axis length between successive ellipses, and we use the median pixel value over the
    elliptical annulus after rejecting outlier pixels twice with $3\sigma$-clipping.
    These parameters are selected to make the final profile less affected by any nearby
    objects, and please see Appendix.~B for more details about the extraction of 
    1-D profile. 
    Fig.~5 shows one example of the 1-D measurement, where we also compare the profile 
    of the galaxy with the PSF profile extracted using circular aperture.

    It is worth noting that, can not extract reliable 1-D profiles for a small fraction 
    of massive galaxies in both samples due to masked-out center that is caused by 
    either physical (e.g.\ late-stage major merger) or unphysical (e.g.\ nearby foreground 
    galaxy or bright star) reasons.  
    For the physically interacting ones, it might be worth studying whether their 
    profiles are different with the relaxed ones, but we have to rely on 2-D 
    decomposition technique for that.

    We correct the surface brightness profiles for Galactic extinction and 
    cosmological dimming, and then integrate them to a series of radii to get the 
    luminosity within different physical apertures.  
    Although the 1-D profile from our $i$-band image can reach to as deep as 
    30 \sb, we often see sudden truncation or large fluctuation of profiles 
    at the very low surface brightness part due to uncertainty from background 
    subtraction or contamination from other objects.  
    Therefore, we only consider the profiles above 28.5 \sb reliable in this 
    work.  
    Using this conservative estimate, we can reliably estimate total luminosity 
    within $\sim 120$ kpc aperture, which is enough for this work.

    We also apply the isophotes derived on $i$-band images to other bands in 
    ``force-photometry'' mode \texttt{Ellipse} run to get rough estimates of 
    color profiles.  
    Without taking the difference in seeing and background into account, 
    these color profiles can not be used for physical discussion. 
    But with the help of $K$-correction from the next section, we show that there 
    is no systematic difference in color gradient between \texttt{redBCG} and 
    \texttt{nonBCG} sample.

%% ------------------------------------------------------------------------------------ %%

\section{Stellar Masses and Stellar Mass Density Profiles}

\subsection{Stellar Masses from SED Fitting}

    As mentioned earlier, we estimate the total stellar mass and the stellar mass 
    density profiles by applying the average \m2l of the galaxy to the 1-D luminosity 
    profiles we just extracted. 
    We use the broadband Spectral Energy Distributions (SEDs) fitting 
    (see \citealt{Walcher2011} for a recent review) code 
    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
    (\citealt{Moustakas2013}) to estimate the average \m2l and $k$-corrections using
    five band \cmodel photometry. 
    The \cmodel photometry not only takes the PSF convolution into account, but 
    also fixes the model parameters of both de~Vaucouleur and exponential components 
    to the ones from a reference filter (mostly $i$ band) except for their amplitudes.
    Therefore, it provides accurate \emph{average} color of the galaxy despite it tends 
    to underestimate the total flux (e.g.\ Huang\etal~in prep.~).
